%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Key Achievements} % Job title
  {Ortto - \emph{Lead DevOps Engineer}} % Organization
  {Sydney, NSW, Australia} % Location
  {August 2021  - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Uplifted the Data Science workflow \& infrastructure with Docker, Buildkite, Terraform, Vault \& GCP}
      \item {Introduced \& championed Kubernetes which is now running all new applications and projects.}
      \item {Streamlined Kubernetes deployments with a Python tool combining Docker, GCR/ECR and Helm.}
      \item {Design, deployment, configuration of monitoring and logging systems.}
      \item {Introduced Chaos Engineering to build high availability into new products.}
      \item {Obtained SOC2 and ISO27001 certifications for the company.}
    \end{cvitems}
  }

  \cventry
  {Environment} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Leading a team of 3 Ops Engineers.}
      \item {End-to-end responsibility: tooling, code builds, infrastructure, deployments, monitoring, and backups.}
      \item {Primarily working on microservices (Kubernetes) and with some monolithic and serverless (Lambda) architecture.}
      \item {Supporting 30 engineers (back-end, front-end and QA), 5000+ customers and 150+ servers.}
      \item {Reporting to CTO.}
    \end{cvitems}
  }

  \cventry
  {Responsibilities} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Manage Amazon Web Services (AWS): EKS, EC2, RDS, S3, Lambda, CloudFront, IAM, Route 53.}
      \item {Manage Kubernetes clusters within EKS and GKE with deployments through Helm and Terraform.}
      \item {Develop and maintain CI/CD pipelines for all projects and their build agents in Buildkite.}
      \item {Building infrastructure using Terraform Enterprise and Packer.}
      \item {Monitoring, logging and alerting with Prometheus, Grafana, Loki, Datadog, PagerDuty, Elasticsearch, Kibana and Beats.}
      \item {Automation and scripting with Bash/Shell, Python and Golang.}
      \item {Security: Authentication, authorisation, bug bounties, SOC2, HIPAA, GDPR, VPNs, Trivy, Anchore and managing security training.}
      \item {Manage Google Cloud Platform (GCP): GCE, GKE, GCS, IAM, LB, Cloud Functions.}
      \item {Manage Rackspace: Cloud VMs.}
      \item {MongoDB Atlas and ScyllaDB Cloud - Cluster management, user management and monitoring.}
      \item {Configuration management using Ansible and AWX (Ansible Tower).}
      \item {Manage internal IT - networking (Ubiquiti), purchases and on/off-boarding.}
    \end{cvitems}
  }

  \cventry
  {} % Job title
  {Ortto - \emph{Senior DevOps Engineer}} % Organization
  {Sydney, NSW, Australia} % Location
  {April 2019 - August 2021} % Date(s)
  {}

  %---------------------------------------------------------
  \cventry
  {Key Achievements} % Job title
  {Coates Group - \emph{DevOps Engineer}} % Organization
  {Alexandria, NSW, Australia} % Location
  {October 2017 - April 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Design of Elastic Stack (ELK) deployment using Saltstack for log management.}
      \item {Design and development of AWS Load Balancers through CloudFormation with Python (boto3).}
      \item {Design, configuration and migration to RDS Aurora from MySQL with CloudFormation.}
      \item {Introduced Kanban to the team with JIRA and associated agile ceremonies.}
      \item {Automated migration of projects from GitLab.com to GitLab EE (+ Git LFS projects).}
      \item {Co-designed the Release Management process with Git and container orchestration.}
      \item {Implemented SSO/LDAP authentication for all engineering-related tools.}
      \item {Reduced AWS bill with consolidated billing, reserved instances and rightsizing.}
    \end{cvitems}
  }

  \cventry
  {Environment} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Team of 3 Ops Engineers.}
      \item {End-to-end: code builds, infrastructure, deployments, monitoring and backups.}
      \item {Microservices architecture.}
      \item {Supporting 20 developers, 40 customers and 20000 devices (Intel NUCs) worldwide.}
      \item {Reporting to Lead Ops Engineer.}
    \end{cvitems}
  }

  \cventry
  {Responsibilities} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Manage Amazon Web Services (AWS): EC2, RDS, S3, Lambda, IAM, CloudFormation, VPC, SES.}
      \item {Manage Google Cloud Platform (GCP): GSuite, IAM, Billing, SSO via Office 365.}
      \item {Management of GitLab, GitLab CI, Confluence and JIRA.}
      \item {Deployments (Prod \& Internal) using Docker container orchestration (Rancher).}
      \item {Level 3 support for Switchboard CMS software when tickets are escalated through Zendesk.}
      \item {Configuration management using Saltstack.}
      \item {Manage internal network - Sophos, VLANs, Cisco Meraki.}
      \item {Proactive monitoring through Prometheus, AlertManager and Grafana.}
      \item {Automation and scripting with Bash/Shell and Python.}
      \item {Upskilling and training of Ops practices in overseas offices.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Key Achievements} % Job title
  {Commonwealth Bank of Australia - \emph{DevOps Engineer}} % Organization
  {Sydney, NSW, Australia} % Location
  {November 2016 - October 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Engineered an automated build pipeline for creating Vagrant boxes using Packer, Ansible and VirtualBox for local development and testing.}
      \item {Established the team's Git-flow model used for all code repositories.}
      \item {Implementation of JFrog Artifactory, Mission Control and Xray in the bank's production environment and onto AWS.}
      \item {Developed AppDynamics monitors for Artifactory package managers (i.e. Yum, PyPI, Gems, NuGet, etc.) to observe and mimic end-user response times, errors and experience.}    \end{cvitems}
  }

  \cventry
  {Environment} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Team of 6 Engineers.}
      \item {Supporting 8000 bank developers locally and off-shore.}
      \item {Docker, Red Hat 5/6/7, Windows Server 2003-2012, MS SQL.}
    \end{cvitems}
  }

  \cventry
  {Responsibilities} % Job title
  {} % Organization
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Responsible for bank standard CI/CD tools: JFrog Artifactory, SonarQube, NuGet, GitHub Enterprise, Atlassian BitBucket Server and JetBrains TeamCity.}
      \item {Provide 3rd level support and training of CI/CD tools listed previously.}
      \item {Consulting, promoting and implementing tools and processes that automate the flow of code through tools listed above.}
      \item {Provide consultancy and engineering for projects in regards to CI/CD.}
      \item {Developing and using Ansible scripts to automate workflows.}
      \item {Monitoring and logging of services using AppDynamics and Splunk.}
      \item {Issue tracking and Scrum sprint management using Atlassian JIRA and Confluence.}
    \end{cvitems}
  }

  \cventry
  {} % Job title
  {Commonwealth Bank of Australia - \emph{Graduate}} % Organization
  {Sydney, NSW, Australia} % Location
  {February 2016 - November 2016} % Date(s)
  {}

  %---------------------------------------------------------

  \cventry
  {} % Job title
  {E-Flo Computers - \emph{Technical Support Officer}} % Organization
  {Sydney, NSW, Australia} % Location
  {March 2015 - December 2015} % Date(s)
  {}

  %---------------------------------------------------------

  \cventry
  {} % Job title
  {IBM - \emph{Innovations Center Technical Intern}} % Organization
  {St. Leonards, NSW, Australia} % Location
  {February 2014 - February 2015} % Date(s)
  {}

  %---------------------------------------------------------
\end{cventries}
